% The FLFishery package for modelling fishing fleets
% Iago Mosqueira & Finlay Scott EC JRC\protect\thanks{
	European Commission\\
	Joint Research Center\\
	IPSC - Maritime Affairs Unit G04\\
	Ispra, Italy\\
	\url{https://fishreg.jrc.ec.europa.eu/}} - FLR Project
% `r format(as.Date(system("git log -1 --format=%ci ggplotFL.Rmd", intern=TRUE)), "%B %Y")`

<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{The FLFishery package for modelling fishing fleets}
-->

```{r, setup, echo=FALSE, results='hide', message=FALSE}
library(knitr)
opts_chunk$set(dev='pdf', cache=TRUE, fig.width=4.5, fig.height=4.5, tidy=TRUE)
options(width=50)
```

```{r, load, echo=FALSE, results='hide', message=FALSE}
library(FLFishery)
```

# Classes

## FLCatch

## FLCatches

## FLFishery

## FLFisheries

# Methods

## plot

## coercion

# Examples

# References

# More information

* You can submit bug reports, questions or suggestions on `FLFishery` at the `FLFishery` issue page ^[<https://github.com/flr/FLFishery/issues>], or on the *FLR* mailing list.
* Or send a pull request to <https://github.com/flr/FLFishery/>
* For more information on the FLR Project for Quantitative Fisheries Science in R, visit the FLR webpage ^[<http://flr-project.org>].
* The latest version of `FLFishery` can always be installed using the `devtools` package, by calling
```{r, devtools, echo=TRUE, eval=FALSE}
	library(devtools)
	install_github('FLFishery', 'flr')
```

## Software Versions

* `r version$version.string`
* FLFishery: `r packageVersion('FLFishery')`
* FLCore: `r packageVersion('FLCore')`
* **Compiled**: `r date()`
* **Git Hash**: `r system("git log --pretty=format:'%h' -n 1", intern=TRUE)`

## `knitr` options

```{r setupf, ref.label='setup', echo=2, eval=FALSE}
```
